Home Nighttime Cough Monitoring

### 2025-03-13 Lilah Melzer/cough_monitor_analysis.qmd
new figures for Lilah

```{r setup}
#| include: false
library(Hmisc)
library(redcapAPI)
library(rspiro)
library(childsds)
library(arsenal)
library(lmerTest)
library(performance)
library(GLMMadaptive)
library(tidyverse)
library(ggstats)
library(corrplot)
library(patchwork)
library(gt)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Lilah Melzer/Lilah Cough Monitor",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF/Lilah Melzer/Lilah Cough Monitor"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Documents/GitHub",
  "Linux" = "/home/timvigers/Documents/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r}
#| label: fig-coughs-dist
#| fig-cap: Histogram of Coughs Across All Nights
#| warning: false
hist <- ggplot(agg_counts, aes(x = Coughs)) +
  geom_histogram() +
  theme_bw() +
  theme(axis.title.y = element_blank())
hist
ggsave(paste0(home_dir, "/Dissemination/Figures/histogram.png"),
  plot = hist, width = 9, height = 6, units = "in"
)
```

@@

```{r}
#| label: fig-coughs-by-night
#| fig-cap: Coughs by nights from start
#| warning: false
fig2 <- ggplot(agg_counts[!is.na(agg_counts$Coughs), ], aes(
  x = Night, y = Coughs, group = factor(sid), color = Diagnosis
)) +
  geom_point(alpha = 0.1) +
  geom_line(alpha = 0.1) +
  geom_smooth(aes(group = Diagnosis)) +
  theme_bw()
fig2
ggsave(paste0(home_dir, "/Dissemination/Figures/fig2.png"),
  plot = fig2, width = 9, height = 6, units = "in"
)
```

>>>>

```{r setup}
#| include: false
library(Hmisc)
library(redcapAPI)
library(rspiro)
library(childsds)
library(arsenal)
library(lmerTest)
library(performance)
library(GLMMadaptive)
library(tidyverse)
library(ggstats)
library(corrplot)
library(patchwork)
library(gt)
library(ggbreak)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Lilah Melzer/Lilah Cough Monitor",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF/Lilah Melzer/Lilah Cough Monitor"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Documents/GitHub",
  "Linux" = "/home/timvigers/Documents/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

```{r}
#| label: fig-coughs-dist
#| fig-cap: Histogram of Coughs Across All Nights
#| warning: false
hist <- ggplot(agg_counts, aes(x = Coughs)) +
  geom_histogram() +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  facet_wrap(~Diagnosis, scales = "free_x")
hist
ggsave(paste0(home_dir, "/Dissemination/Figures/histogram.png"),
  plot = hist, width = 9, height = 6, units = "in"
)
```

@@

```{r}
#| label: fig-coughs-by-night
#| fig-cap: Coughs by nights from start
#| warning: false
fig2 <- ggplot(agg_counts[!is.na(agg_counts$Coughs), ], aes(
  x = Night, y = Coughs, group = factor(sid), color = Diagnosis
)) +
  geom_point(alpha = 0.2) +
  geom_line(alpha = 0.2) +
  geom_smooth(aes(group = Diagnosis)) +
  ylim(c(1, 275)) +
  xlim(c(0, 100)) +
  theme_bw() +
  scale_color_manual(values = c("#003092", "#FFAB5B")) +
  scale_y_break(c(80, 265), scales = 0.25, ticklabels = c(265, 270, 275))
fig2
ggsave(paste0(home_dir, "/Dissemination/Figures/fig2.png"),
  plot = fig2, width = 9, height = 6, units = "in"
)
```
